Races with hyper3 objects

### 2022-07-28 inst/race3.Rmd
bugfix

>>>>

## Constructors championship with `cheering` or `tether` functionality

```{r,Bahrain2021_to_support3}
constructor_2021_table
(cons <- constructor_2021_table[,1])
(BHR <- as.numeric(constructor_2021_table[,2]))  # Bahrain
names(BHR) <- cons
BHR
finishers <- BHR[!is.na(BHR)]
finishers <- names(finishers[order(finishers)])  # in order
nonfinishers <- names(BHR[is.na(BHR)])  # no particular order
finishers
nonfinishers
u <- unique(c(finishers,nonfinishers))
e <- seq_along(u)
names(e) <- u
e
help <- rep(1.8,length(u))
e
help
cheering3(v=finishers,e=e,help=help,nonfinishers=nonfinishers)
```

OK so now generalize it:

```{r,definevenue3}
venue3 <- function(ven,cons,help){
   suppressWarnings(names(ven) <- cons)
   finishers <- ven[!is.na(ven)]
   finishers <- names(finishers[order(finishers)])  # in order
   nonfinishers <- names(ven[is.na(ven)])  # no particular order
   u <- unique(c(finishers,nonfinishers))
   e <- seq_along(u)
   names(e) <- u
   help <- rep(help,length(u))
   cheering3(v=finishers,e=e,help=help,nonfinishers=nonfinishers)
}  # venue3() definition closes
```

Now use `venue3()` for all the venues in the 2021 season, with a common help:

```{r,defineallvenues,cache=TRUE}
set.seed(9)
allvenues <- function(h){
  H3 <- hyper3()
  cons <- constructor_2021_table[,1]
  for(i in seq(from=2,to=ncol(constructor_2021_table),by=1)){
     H3 <- H3 + venue3(ven=as.numeric(constructor_2021_table[,i]), cons=cons,help=h)
  }
  return(H3)
}
## And maximize it for different help values:

o <- function(h){maxp(allvenues(h),give=TRUE,n=1)$likes}
l <- seq(from=0.9,to=4,len=11)
L <- sapply(l,o)
```

```{r,plotsupport}
plot(l,L-max(L),type='b')
```

Above, we are testing (and rejecting) the hypothesis that the various
constructors are independent of one another.  We reject the hypothesis
that $h=1$.  Noting that we control both for constructors'
Plackett-Luce strengths, and on the assumption that the two drivers of
any given constructor are of equal strengths, we still reject the
hypothesis of conditional independence.

```{r,label=maxwithfour,cache=TRUE}
o <- maxp(allvenues(4),give=TRUE,n=1,hessian=TRUE)
```

```{r,analyse4}
pie(o$par)
eigen(o$hessian)$values
```
